Process_OlisSpectraJazEmData

### 2024-01-04 Code/Process_OlisJazEmData.Rmd
Fixing more code to include all WL normalization.

#Left off here
```{r}
JazEmFile <- JazEmFile %>% 
  filter(MC_SpectralID != "MCMIX004_WW",
         MCSetPar_uE == 30 ) %>% 
  select(-c( FilenameJaz, MC)) %>% 
  unnest(Spectra) %>%  
  group_by(WL) %>% 
  mutate(MC_NormEm = round(Emission / Emission[which.max(Emission)], digits = 4)) %>% 
ungroup()
```

>>>>

# Filter out the white light emission data for mixed light color MC since not used. Calculate MC normalized emission to the emission maxima for each wavelength.
```{r calculate normalized emission for each WL}
JazEmFile <- JazEmFile %>% 
  filter(MC_SpectralID != "MCMIX004_WW",
         MCSetPar_uE == 30 |
         MCSetPar_uE == 15) %>% 
  select(-c( FilenameJaz, MC)) %>% 
  unnest(Spectra) %>%  
  group_by(WL) %>% 
  mutate(MC_NormEm = round(Emission / Emission[which.max(Emission)], digits = 4)) %>% 
  select(-c(ObsDate)) %>% 
ungroup()
```

# Unnest the Olis whole cell absorbance data and calculate absorbance maxima for 675 nm (red) and 450 (blue) and extract nm (wavelength) at maxima 
```{r}
OLISSpectraUnnest <- OLISSpectraFile %>% 
  unnest(AbsSpectra)

OlisSpectra_red <- OLISSpectraUnnest %>% 
  group_by(SampleID, E_days) %>%
  filter(OlisAbs_nm >= 575 & OlisAbs_nm <= 750) %>% 
   mutate(Red_nm = round(OlisAbs_nm[which.max(Absorbance)]),
          MaxAbs_Red = Absorbance[which.max(Absorbance)]) %>% 
  filter(OlisAbs_nm == 675) %>% 
  select(SampleID, Run, Strain, Red_nm, MaxAbs_Red, Par_ue, E_days) %>% 
     ungroup()

OlisSpectra_blue <- OLISSpectraUnnest %>% 
  group_by(SampleID, E_days) %>%
  filter(OlisAbs_nm >= 400 & OlisAbs_nm <= 460) %>% 
   mutate(Blue_nm = round(OlisAbs_nm[which.max(Absorbance)]),
          MaxAbs_Blue = Absorbance[which.max(Absorbance)])  %>% 
  filter(OlisAbs_nm == 440) %>% 
  select(SampleID, Run, Strain, Blue_nm, MaxAbs_Blue,  Par_ue, E_days) %>% 
  ungroup()

OLISSpectraFile <- OLISSpectraFile %>%
  group_by(SampleID, E_days) %>%
  nest(AbsSpectra = c(OlisAbs_nm, Absorbance))

 OlisSpectraMeta_red <- left_join(OLISSpectraFile, OlisSpectra_red)

# Left join Olis whole cell absorbance data with Jaz MC emission data. Emission measurements were performed on the mixed color MCMIX004 and the white light MC257
```{r join whole cell absorbance with MC emission data}

OlisJazMetaData <- left_join(OLISSpectraFile , JazEmFile, by = c("WL", "OlisAbs_nm" = "MCEm_nm")) %>% 
  mutate(MCEm_nm = OlisAbs_nm)
```
